### 2018-08-09 TeX/organigram2.tex
additional changes

%arrows
\tikzstyle{arrow} = [->, > = stealth, draw = black, color = yellow!80, line width = 6pt]
% TODO double colored arrows - don't know how it works
\iffalse
\tikzset{
	darrow/.style args={#1 colored by #2 and #3}{
		-stealth,line width=#1,#2, % first arrow
		postaction={draw,-stealth,#3,line width=(#1)/3,
			shorten <=(#1)/3,shorten >=2*(#1)/3}, % second arrow
	}
}
\fi

@@

%%% nodes %%%
%% input
% TODO coordinates (-3,4) is strange. Also rectangle around current page seems wrong
\node[text=red] (io) [io, align = left] at (-3,4) {Table of Chemicals \\ CAS, Compound name}; % coordinates: (current page.east)

@@

%% chemicals
% id nodes
\node (cas) [ids, below of=io, yshift = -4cm] {CAS};
% main nodes
\node (chemprop) [main, dashed, right of=cas, xshift=4.5cm, yshift=3cm] {CHEMPROP};
\node (epa) [main, right of=cas, yshift=1cm, xshift=4.5cm] {EPA ectox tests}
	child { node { qu\_epa.R} };
\node (chemscr) [main, right of=cas, yshift=-1cm, xshift=4.5cm] {Chemical scripts ch}
	child { node { Alan Wood Pesticide Compendium - \textbf{qu\_aw.R } }}
	child { node { Pesticide Action Network - \textbf{ch\_pp.R} }}
	child { node { PhysProp - \textbf{ch\_pp.R} }}
	child { node { PubChem - \textbf{qu\_pubchem.R} }};
% result nodes
\node (toxres) [resvariables, right of=cas, yshift=0cm, xshift=16cm, align = left] {Results\\Test results\\Substance type:\\pesticides, metals, etc.}; % result
%\includegraphics{/home/andreas/Documents/Projects/etox-base/data/pubchemlogo2017.png};

@@

%% final result
\node (testres) [res] at (16,-5) {Final result}
	child { node { re\_merge.R} };
\iffalse
node[anchor = south]
node[anchor = east]
\fi

@@

\draw [arrow, dashed] (testres) -- (20,-5);
\end{pgfonlayer}

\end{tikzpicture}
\hfill
\vfill
\end{landscape}

%\clearpage

@@

%% entities
\node (clean) [res] at (-5,5) {Cleaning}
	child { node { re\_clean.R} };
\node (filter) [res, right of = clean, xshift = 3cm] {Filter}
	child { node { re\_filter.R} };
\node (plot) [res, right of = filter, xshift = 3cm] {Plots}
	child { node { re\_plot.R} };
\node (agg1) [res, right of = plot, xshift = 3cm] {Aggregation};

>>>>

%arrows
\tikzstyle{arrow} = [->, > = stealth, draw = black, color = yellow!80, line width = 6pt]

@@

%%% nodes %%%
%% input
% TODO coordinates (-3,4) is strange. Also rectangle around current page seems wrong
\node[text=red] (io) [io, align = left] at (-3cm,4cm) {Table of Chemicals \\ CAS, Compound name}; % coordinates: (current page.east)

@@

%% chemicals
% id nodes
\node (cas) [ids, below of=io, yshift = -4cm] {CAS};
% main nodes
\node (chemprop) [main, dashed, right of=cas, xshift=4.5cm, yshift=3cm] {CHEMPROP};
\node (epa) [main, right of=cas, yshift=1cm, xshift=4.5cm] {EPA ectox tests}
	child { node { qu\_epa.R} };
\node (chemscr) [main, right of=cas, yshift=-1cm, xshift=4.5cm] {Chemical scripts ch}
	child { node { Alan Wood Pesticide Compendium - \textbf{qu\_aw.R } }}
	child { node { Pesticide Action Network - \textbf{ch\_pan.R} }}
	child { node { PhysProp - \textbf{ch\_pp.R} }}
	child { node { PubChem - \textbf{qu\_pubchem.R} }};
% result nodes
\node (toxres) [resvariables, right of=cas, yshift=0cm, xshift=16cm, align = left] {Results\\Test results\\Substance type:\\pesticides, metals, etc.}; % result
%\includegraphics{/home/andreas/Documents/Projects/etox-base/data/pubchemlogo2017.png};

@@

%% final result
\node (testres) [res] at (18,-5) {Final result}
	child { node { re\_merge.R} };
\iffalse
node[anchor = south]
node[anchor = east]
\fi

@@

\draw [arrow] (testres) -- (22,-5);
\end{pgfonlayer}

%\clearpage
%\thispagestyle{empty} % removes the 1

@@

%\draw[thick] (current page.south west) rectangle (current page.north east); % debuging

%% entities
\node (test) [res] at (-10,-10) {Test}; %debuging

\node (clean) [res] at (-5,5) {Cleaning}
	child { node { re\_clean.R} };
\node (filter) [res, right of = clean, xshift = 3cm] {Filter}
	child { node { re\_filter.R} };
\node (plot) [res, right of = filter, xshift = 3cm] {Plots}
	child { node { re\_plot.R} };
\node (agg1) [res, right of = plot, xshift = 3cm] {Aggregation};
